### 2020-03-20 ChapterResults/chapterResults.tex
Updated: Proof-read of Results

\chapter{Experiments and Results}\label{Results}
In this chapter, experiments for testing both the scalability and correctness of AP are designed and justified, the results of which, are analysed and evaluated. Scalability experiments are carried out with increasing numbers of servers in both column and corner topologies. Correctness experiments are carried out using two servers and two objects, one from each server, colliding with each other under different conditions and with different tolerances used for the aura calculation.

@@

		\clip(-7,0.575) rectangle (7,0.9);
\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (-2.5,0.8) -- (-2.3,0.8) -- (-2.3,0.6) -- (-2.5,0.6) -- cycle;
\draw [line width=0.8pt,color=rvwvcq] (-2.5,0.8)-- (-2.3,0.8);
\draw [line width=0.8pt,color=rvwvcq] (-2.3,0.8)-- (-2.3,0.6);
\draw [line width=0.8pt,color=rvwvcq] (-2.3,0.6)-- (-2.5,0.6);
\draw [line width=0.8pt,color=rvwvcq] (-2.5,0.6)-- (-2.5,0.8);
\draw (-2.1,0.7) node[anchor=west] {Injection Volume};

\draw [line width=2pt] (-6.5,0.7)-- (-6.3,0.7);
\draw (-6.1,0.7) node[anchor=west] {Region Boundary};
\end{tikzpicture}
\caption{Column Layout}
\label{ColumnLayout}
\end{figure}

@@

Experiments were also carried out using servers in a corner layout. The layouts of 3 and 4 servers are shown in Fig. \ref{ServerCorner}, in which the 4 server case is a 2x2 grid with a single corner intersection in the centre. The 9 server case is a 3x3 grid with 4 corner intersections. Injection rates and volume dimensions remain the same as in the column based experiments. Fig. \ref{fig_PerCor} shows the graph describing performance. The graph demonstrates that increasing the number of servers lowers the frame time. The additional processing overhead of exchanging more messages with more neighbouring servers in the 9 server experiment is outweighed by the performance gains of additional servers.

@@

The following points highlight the contributions of the correctness experiments:
\begin{itemize}
	\item Demonstrate that collisions between objects and migrating are handled correctly as long as the factors (speed, frame-time, latency) remain within their tolerances. Collisions can be handled correctly under worsening conditions (higher speed, frame-time and latency), so long as the tolerances account for these.
	\item Demonstrate that late collisions begin to occur once tolerances are exceeded or as predicted by the aura calculation, i.e. auras are the size they need to be, and no larger, which would impact on performance.
	\item Demonstrate the severity of each of the factors being exceeded, i.e. when different factors are exceeded, how badly are collisions handled?
	\item Measure the frequency of two-object-thrashing
\end{itemize}

Experiments were undertaken to detect erroneous collisions under different conditions and are concerned with objects that are migrating and/or interacting with an object that has recently migrated. Erroneous collisions fall into two categories:
\begin{itemize}
	\item Missed collisions, collisions that should have taken place but were not detected by the physics engine e.g. Bullet through paper problem.
	\item Late collisions, collisions that were detected later than expected in a centralised simulation and result in not only different collision results, but also unstable collision response.
\end{itemize}

@@

It will now be explained how a naïve system can lead to erroneous collision behaviour and AP can lead to erroneous collision behaviour if speed, frame-time, or latency exceed the user-defined tolerances.

In a hypothetical naïve system, a system that does not use AP, objects are migrated solely based on their position and objects on a remote server are not accounted for. Two objects close to the server region boundary could be occupying the same space at the same time. If one object were to be migrated to the other server, for example if the centre of the object has traversed the region boundary, then the object would be migrated into an overlapping space as the other object on the receiving server. This penetration could be much greater than would be expected in a normal collision detection and could lead to a highly erroneous collision response.

@@

Thrashing between two objects on different servers is an unsolved problem in AP; thrashing occurrences can be detected by counting the number of migrations that occur before the first collision is detected, as only two objects are involved in each experiment, the number of migrations before a collision should only be one, otherwise thrashing has occurred. For the purposes of these experiments, collisions involving thrashing will be excluded, regardless of the correctness of the collision.

@@

As speed increases, expected penetration increases. Using penetration time gives us a uniform maximum expected value regardless of speed.
Re-arranging $s=d/t$, to $t=d/s$ and substituting the collision penetration for $d$ and speed for $s$, gives us the penetration time for a collision. It should be noted that because physics engines work in discrete time steps, this time value does not actually reflect the real time the colliding objects were penetrating each other. Also note that PhysX can report collisions before objects intersect, leading to the negative penetration distances shown. Correct collisions result in penetration times of up to 1 physics time step and any collision penetration times over this value are considered erroneous. Fig. \ref{fig_ErrorControlTime} shows the penetration of objects with increasing speed in a centralised simulation (displaying speed without the random variation) and demonstrates that penetration time is never greater than the time of one physics step, regardless of the relative speed of objects. The purpose of this experiment was to confirm the predicted maximum expected penetration in a centralised simulation. This provides a benchmark of correctness to compare with results from experiments using multiple servers.

@@

In order t rigorously test the hypothesis "Can real-time physics simulations remain correct when scaled?", a `worst-case' scenario was used for the experiments, in which two objects are moving directly towards each other and collide while one of the objects is intersecting the boundary between servers. In this experiment two servers were used with one sphere being created on each server. The two spheres were given starting positions so the two would collide at a point when one of the spheres is intersecting the server region boundary, thus creating the most likely situation for spheres collide with each other in the first time-step after being migrated; this is necessary as AP can only lead to late or missed collisions when at least one sphere involved in the collision has just migrated (received since the last physics time-step). This is because non-migrating spheres behave the same as spheres in a centralised solution, therefore only collisions that involve a sphere that has just migrated are considered in the experiment results.

\begin{figure}
	\centering
	\includegraphics[width=0.75\textwidth]{CorrectnessExperiment}
	\caption{Correctness Experiment setup. The setup is the `worst-case' scenario, in which two objects are moving directly towards each other and collide while one of the objects is intersecting the boundary between servers.}
	\label{fig_CorrectnessExperiment}
\end{figure}

@@

Fig. \ref{fig_FrameTimeAuraSize} shows the size of the aura (not including the bounding sphere of the object) vs increasing frame-time tolerance, calculated using equation \ref{auraEquation}. The aura size increases discretely with frame-time tolerance, therefore we expect late collisions to begin one the aura size required for the latency is higher than what is needed for the tolerance. In the varying frame-time experiments, this will be when frame-time reaches $16ms$ for the $8ms$ and $15ms$ tolerance experiments and $32ms$ for the $32ms$ tolerance experiment. Note that late collisions are not expected for the $8ms$ experiment, as $16ms$ frame-time is not exceeded. False-positives are expected due to the frame-time delay method and should increase as frame-time increases.

@@

\begin{table}
	\centering
	\begin{tabular}{llrrrr}
		\toprule
		\multicolumn{1}{l}{Factor} & \multicolumn{1}{l}{Tolerance} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Late \%} & \multicolumn{1}{l}{Miss \%} & \multicolumn{1}{l}{Thrashing}  \\ 
		\hline
		Speed      & 16m/s     & 800  & 1     & 0.13       &    0             \\
		Speed      & 32m/s     & 1600 & 0.688 & 0.0422     &    0             \\
		Speed      & 48m/s     & 2372  & 0.632& 0          &    28            \\
		Latency    & 2ms       & 1920  & 10.7 & 0          &    7             \\
		Latency    & 8ms       & 1520  & 0    & 0          &    30            \\
		Latency    & 16ms      & 797  & 2.50  & 0          &    53            \\
		Frame-Time & 8.33ms    & 450  & 0     & 0          &    0             \\
		Frame-Time & 15ms      & 800  & 1.88  & 0          &    0             \\
		Frame-Time & 33.33ms   & 251  & 0     & 0          &    523           \\
		\bottomrule
	\end{tabular}
	\caption{Below Tolerance}
	\label{tab_BelowTolerance}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{llrrrr}
		\toprule
		\multicolumn{1}{l}{Factor} & \multicolumn{1}{l}{Tolerance} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Late \%} & \multicolumn{1}{l}{Miss \%} & \multicolumn{1}{l}{Thrashing}  \\ 
		\hline
		Speed      & 16m/s     & 800  &   49.9  & 0           & 0               \\
		Speed      & 32m/s     & 1589  &  48.6  & 0           & 11              \\
		Speed      & 48m/s     & 2233  &  45.10 & 1.12        & 167             \\
		Latency    & 2ms       & 1880  &  13.99 & 0           & 0               \\
		Latency    & 8ms       & 1377  &  0.15  & 0           & 121             \\
		Latency    & 16ms      & 574  &   12.20 & 0           & 226             \\
		Frame-Time & 8.33ms    & 400  &   9.50  & 0           & 0               \\
		Frame-Time & 15ms      & 750  &   58.13 & 0           & 0               \\
		Frame-Time & 33.33ms   & 106  &   1.89  & 0           & 693             \\
		\bottomrule
	\end{tabular}
	\caption{Above Tolerance}
	\label{tab_AboveTolerance}
\end{table}

@@

The more times thrashing occurs, the later the collision may be detected as objects continue to be updated and move without a collision occurring. It should be noted that thrashing occurring does not guarantee that a late collision will take place. The more times thrashing takes place, the more physics updates occur and the further the objects may be moved towards (and eventually overlapping) each other. Therefore, a greater number of times thrashed, means a late and incorrect collision response is more likely.

@@

\subsubsection{Evaluation - Speed}
As the speed increases, the proportion of late collisions to correct collisions increases, as shown in Figs. \ref{fig_RatioVsSpeedLow}, \ref{fig_RatioVsSpeedMid} and \ref{fig_RatioVsSpeedHigh}. When speed is below the speed tolerance, late collisions do not exceed 10\%. This 10\% can be accounted for by false-positives. Once above the speed tolerance, the proportion of late collisions increases immediately, which is predicted by the aura calculation. Missed collisions begin to occur when speed exceed $80ms^{-1}$ in the $48ms^{-1}$ experiment, this is due to objects travelling so quickly, the objects completely pass one another, missing the collision entirely.

@@

As the speed increases, the mean penetration time increases, as shown in Figs. \ref{fig_CollisionsPenVsSpeedLow}, \ref{fig_CollisionsPenVsSpeedMid} and \ref{fig_CollisionsPenVsSpeedHigh}. With the exception of the starting speed, the standard deviation remains constant below the tolerance line. Once speed increases above the tolerance line, the standard deviation initially increases, but appears to remain constant after the initial increase. Note that the mean error increases in discrete steps (with some small variation), this is due to the discrete physics time-steps.

\subsubsection{Evaluation - Latency}
As the latency increases, the proportion of late collisions to correct collisions increases, as shown in Fig. \ref{fig_RatioVsLatencyHigh}. However, Figs. \ref{fig_RatioVsLatencyLow} and \ref{fig_RatioVsLatencyLow} do not show this relationship. In the $2ms$ latency tolerance experiment, late collisions do not exceed $20\%$, which can be accounted for by false-positives. The aura calculation predicts that late collisions should start occurring once $3ms$ has been exceeded, however, this is not observed, as the proportion does not increase above what would be expected for false-positives.
In the $8ms$ latency tolerance experiment, late collisions do not exceed $2\%$, which can be accounted for by false-positives. This remains the case even when the tolerance is exceeded. The aura calculation predicts that late collisions will not begin to occur until $20ms$ latency is reached, which this experiment does not reach, therefore no late collisions outside of false-positives are expected. In the $16ms$ latency tolerance experiment, late collisions do not exceed $3\%$ below the tolerance, which can be accounted for by false-positives. The aura calculation predicts that late collisions will not begin to occur until $20ms$ latency is reached. In Fig. \ref{fig_RatioVsLatencyHigh} we see the proportion of errors increase from $20ms$ and above, however, it does not exceed the expected false-positive proportion until $25ms$ latency is reached.
%TODO: Re-run latency experiment, larger sample size?

@@

\subsubsection{Evaluation - Frame-Time}
As frame-time increases, the proportion of late collisions to correct collisions increases, as shown in Figs. \ref{fig_RatioVsLatencyLow} and \ref{fig_RatioVsLatencyMid}, however in \ref{fig_RatioVsLatencyHigh} the sample size is small above the tolerance line due to the high occurrences of thrashing and so the relationship in this experiment can not be deduced. For the $8ms$ and $15ms$ experiments the late collisions do not exceed 10\% and these can be accounted for by false-positives. In the $8ms$ frame-time tolerance experiment, late collisions are not expected to occur until $16ms$ frame-time, based on the aura size. Late collisions do not exceed $20\%$ and these can all be accounted for by false-positives. In the $15ms$ frame-time tolerance experiment, late collisions exceed $20\%$ once $16ms$ latency is exceeded as predicted by the aura size and increase to over $75\%$ at $30ms$ latency.
In the final frame-time tolerance experiment using $32ms$ frame-time tolerance, late collisions only occur for frame-times of $64ms$. The aura calculation predicts that late collisions should begin to occur as soon as $32ms$ frame-time is exceeded, however, due to the low sample size, as a result of the high occurrences of thrashing, the plot does not accurately represent any relationship between frame-time and proportion of late collisions.

For the first two frame-time experiments ($8.33ms$ and $15ms$ tolerance values), as frame-time increases, the mean penetration time increases and standard deviation also increases, shown in Figs. \ref{fig_CollisionsPenVsFrameTimeLow} and \ref{fig_CollisionsPenVsFrameTimeMid}. Standard deviation increases as the delay between frame-time update and physics update can always vary between 0 and the frame-time, meaning even in high frame-time situations, the delay between frame-time update and physics update can be 0. Exceeding the frame-time tolerance very quickly leads to high max error, this is due to the delay in messages being exchanged being created by the long frame-times on both servers (this is reflected in the aura calculation by the frame-time tolerance being multiplied by 2). However, as the target frame-time increases over the tolerance, variation in error increases and max errors become less likely. For the final frame-time experiment, ($33.33ms$ tolerance value), thrashing occurs the majority of the time both above (as demonstrated in \ref{tab_BelowTolerance} and \ref{tab_AboveTolerance}) and below the tolerance, due to this the results shown in \ref{fig_CollisionsPenVsFrameTimeHigh} have a very small sample size and thus will not accurately represent the relationship between frame-time and penetration.

\subsubsection{Summary}
The varying factors experiments demonstrate that the aura calculation is correct for all aura tolerance factors. For each varied factor, for all three tolerance values chosen, below the tolerance value, the mean + two standard deviations lies under the maximum penetration time expected on a centralised simulation, with only a small number of exceptions discussed above. These experiments also demonstrate the relationship between increasing the tolerance values and amount of thrashing expected to occur. There are no missed collisions, with the exception of the speed experiments, which have significantly fewer than $1\%$ misses below the tolerance and $1.12\%$ misses above the tolerance. Once factors increase above their respective tolerance values, late collisions begin to occur and the more the factors are exceeded, the number and magnitude of errors increase. This demonstrates the correctness of the aura calculation in AP.
%Therefore, we have shown that if the aura calculation factors remain within their respective tolerances, erroneous collisions will be small in magnitude and rare in number. %TODO: Summary Table: Row for each factor: Number of collisions below tolerance, Percentage of errors below tolerance, Mean error below tolerance

@@

In addition to varying each aura tolerance factor, an experiment was undertaken to determine the effects of packet-loss on the correctness of collisions between objects. In this experiment the packet-loss was varied from $0\%$ to $20\%$ in increments of $1\%$. The aura calculation does not account for packet-loss and and therefore there is no tolerance. Packet-loss is controlled using the Traffic Control tool; it is simulated on each server for all communication received from the other server.

@@

\subsubsection{Evaluation}
As packet-loss increases, late and erroneous collisions increase and late collisions increase in magnitude. This is due to messages being delayed as packets are lost and need to be re-sent by RakNet's reliability layer. Missed collisions begin to occur as soon as packet-loss exceeds $1\%$, but increase at a lower rate relative to late collisions. (Note, late collisions begin to occur from $0\%$, this is expected as all factors are set to be equal to their tolerances). These results demonstrate that AP is able to prevent $50\%$ of late collisions even in cases of packet-loss as high as (15\%) and prevent all missed collisions with up to $1\%$ packet-loss, which is much greater than would be expected in practice (0.01\%) \cite{ThousandEyesCloudPerf2018}.

>>>>

\chapter{Experiments and Results}\label{Results}
In this chapter, the design for the experiments for testing both the scalability and correctness of AP are presented and justified, the results of which, are analysed and evaluated. Scalability experiments are carried out with increasing numbers of servers in both column and corner topologies. Correctness experiments are carried out using two servers and two objects, one from each server, colliding with each other under different conditions and with different tolerances used for the aura calculation.

@@

		\clip(-7,0.4) rectangle (7,1.1);
\fill[line width=0.8pt,color=rvwvcq,fill=rvwvcq,fill opacity=0.1] (0.5,0.8) -- (0.7,0.8) -- (0.7,0.6) -- (0.5,0.6) -- cycle;
\draw [line width=0.8pt,color=rvwvcq] (0.5,0.8)-- (0.7,0.8);
\draw [line width=0.8pt,color=rvwvcq] (0.7,0.8)-- (0.7,0.6);
\draw [line width=0.8pt,color=rvwvcq] (0.7,0.6)-- (0.5,0.6);
\draw [line width=0.8pt,color=rvwvcq] (0.5,0.6)-- (0.5,0.8);
\draw (1.0,0.65) node[anchor=west] {Injection Volume};

\draw [line width=2pt] (-4.5,0.7)-- (-4.3,0.7);
\draw (-4.1,0.7) node[anchor=west] {Region Boundary};
\end{tikzpicture}
\caption{Column Layout Experiment Setup}
\label{ColumnLayout}
\end{figure}

@@

Experiments were also carried out using servers in a corner layout. The layouts of 3 and 4 servers are shown in Fig. \ref{ServerCorner}, in which the 4 server case is a 2x2 grid with a single corner intersection in the centre. The 9 server case is a 3x3 grid with 4 corner intersections. Injection rates and volume dimensions remain the same as in the column based experiments. Fig. \ref{fig_PerCor} shows the graph illustrating performance. The graph demonstrates that increasing the number of servers lowers the frame time. The additional processing overhead of exchanging more messages with more neighbouring servers in the 9 server experiment is outweighed by the performance gains of additional servers.

@@

The following points highlight the contributions of the correctness experiments:
\begin{itemize}
	\item Demonstrate that collisions between objects and migrating are handled correctly as long as the factors (speed, frame-time, latency) remain within their tolerances. Collisions can be handled correctly under worsening conditions (higher object speed, frame-time and latency), so long as the tolerances account for these.
	\item Demonstrate that late collisions begin to occur once tolerances are exceeded or as predicted by the aura calculation, i.e. auras are the size they need to be, and no larger, which would impact on performance.
	\item Demonstrate the severity of each of the factors being exceeded, i.e. when different factors are exceeded, how badly are collisions handled?
	\item Measure the frequency of two-object-thrashing
\end{itemize}

Experiments were undertaken to detect erroneous collisions under different conditions and are concerned with objects that are migrating and/or interacting with an object that has recently migrated. Erroneous collisions fall into two categories:
\begin{itemize}
	\item Missed collisions - collisions that should have taken place but were not detected by the physics engine e.g. Bullet through paper problem.
	\item Late collisions - collisions that were detected later than expected in a centralised simulation and result in not only different collision results, but also unstable collision response.
\end{itemize}

@@

It will now be explained how a naive system can lead to erroneous collision behaviour and AP can lead to erroneous collision behaviour if speed, frame-time, or latency exceed the user-defined tolerances.

In a hypothetical naive system, a system that does not use AP, objects are migrated solely based on their position and objects on a remote server are not accounted for. Two objects close to the server region boundary could be occupying the same space at the same time. If one object were to be migrated to the other server, for example, if the centre of the object has traversed the region boundary, then the object would be migrated into an overlapping space as the other object on the receiving server. This penetration could be much greater than would be expected in a normal collision detection and could lead to a highly erroneous collision response.

@@

Thrashing between two objects on different servers is an unsolved problem in AP; thrashing occurrences can be detected by counting the number of migrations that occur before the first collision is detected, as only two objects are involved in each experiment, the number of migrations before a collision should only be one, otherwise thrashing has occurred. For the purposes of these experiments, collisions involving thrashing will be excluded, regardless of the correctness of the collision. Note, for the remainder of this chapter, thrashing refers to only thrashing between two objects and not the solved 3-object-thrashing problem.

@@

As speed increases, expected penetration increases. Using penetration time gives us a uniform maximum expected value regardless of speed.
Re-arranging $s=d/t$, to $t=d/s$ and substituting the collision penetration for $d$ and speed for $s$, gives us the penetration time for a collision. It should be noted that because physics engines work in discrete time steps, this time value does not actually reflect the real time the colliding objects were penetrating each other. It should also be noted that PhysX can report collisions before objects intersect, leading to the negative penetration distances shown. Correct collisions result in penetration times of up to 1 physics time step and any collision penetration times over this value are considered erroneous. Fig. \ref{fig_ErrorControlTime} shows the penetration of objects with increasing speed in a centralised simulation (displaying speed without the random variation) and demonstrates that penetration time is never greater than the time of one physics step, regardless of the relative speed of objects. The purpose of this experiment was to confirm the predicted maximum expected penetration in a centralised simulation. This provides a benchmark of correctness to compare with results from experiments using multiple servers.

@@

In order t rigorously test the hypothesis "Can real-time physics simulations remain correct when scaled?", a `worst-case' scenario was used for the experiments, in which two objects are moving directly towards each other and collide while one of the objects is intersecting the boundary between servers. This experiment setup is illustrated in Fig. \ref{fig_CorrectnessExperiment}. In this experiment two servers were used with one sphere being created on each server. The two spheres were given starting positions so the two would collide at a point when one of the spheres is intersecting the server region boundary, thus creating the most likely situation for spheres collide with each other in the first time-step after being migrated; this is necessary as AP can only lead to late or missed collisions when at least one sphere involved in the collision has just migrated (received since the last physics time-step). This is because non-migrating spheres behave the same as spheres in a centralised solution, therefore only collisions that involve a sphere that has just migrated are considered in the experiment results.

\begin{figure}
	\centering
	\includegraphics[width=0.9\textwidth]{CorrectnessExperiment}
	\caption{Correctness experiment setup. The setup is the `worst-case' scenario, in which two objects are moving directly towards each other and collide while one of the objects is intersecting the boundary between servers.}
	\label{fig_CorrectnessExperiment}
\end{figure}

@@

Fig. \ref{fig_FrameTimeAuraSize} shows the size of the aura (not including the bounding sphere of the object) vs increasing frame-time tolerance, calculated using equation \ref{auraEquation}. The aura size increases discretely with frame-time tolerance, therefore we expect late collisions to begin only once the the actual frame-time is higher than the maximum frame-time the current aura size tolerates. In the varying frame-time experiments, this will be when frame-time reaches $16ms$ for the $8ms$ and $15ms$ tolerance experiments and $32ms$ for the $32ms$ tolerance experiment. Note that late collisions are not expected for the $8ms$ experiment, as $16ms$ frame-time is not exceeded. False-positives are expected due to the frame-time delay method and should increase as frame-time increases.

@@

\begin{table}
	\centering
	\begin{tabular}{llrrrr}
		\toprule
		\multicolumn{1}{l}{Factor} & \multicolumn{1}{l}{Tolerance} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Late \%} & \multicolumn{1}{l}{Miss \%} & \multicolumn{1}{l}{Thrashing}  \\ 
		\hline
		Speed      & 16m/s     & 800  & 1     & 0.13       &    0             \\
		Speed      & 32m/s     & 1600 & 0.688 & 0.0422     &    0             \\
		Speed      & 48m/s     & 2372  & 0.632& 0          &    28            \\
		Latency    & 2ms       & 1920  & 10.7 & 0          &    7             \\
		Latency    & 8ms       & 1520  & 0    & 0          &    30            \\
		Latency    & 16ms      & 797  & 2.50  & 0          &    53            \\
		Frame-Time & 8.33ms    & 450  & 0     & 0          &    0             \\
		Frame-Time & 15ms      & 800  & 1.88  & 0          &    0             \\
		Frame-Time & 33.33ms   & 251  & 0     & 0          &    523           \\
		\bottomrule
	\end{tabular}
	\caption{Results summary of collision correctness experiments before the tolerance was exceeded}
	\label{tab_BelowTolerance}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{llrrrr}
		\toprule
		\multicolumn{1}{l}{Factor} & \multicolumn{1}{l}{Tolerance} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Late \%} & \multicolumn{1}{l}{Miss \%} & \multicolumn{1}{l}{Thrashing}  \\ 
		\hline
		Speed      & 16m/s     & 800  &   49.9  & 0           & 0               \\
		Speed      & 32m/s     & 1589  &  48.6  & 0           & 11              \\
		Speed      & 48m/s     & 2233  &  45.10 & 1.12        & 167             \\
		Latency    & 2ms       & 1880  &  13.99 & 0           & 0               \\
		Latency    & 8ms       & 1377  &  0.15  & 0           & 121             \\
		Latency    & 16ms      & 574  &   12.20 & 0           & 226             \\
		Frame-Time & 8.33ms    & 400  &   9.50  & 0           & 0               \\
		Frame-Time & 15ms      & 750  &   58.13 & 0           & 0               \\
		Frame-Time & 33.33ms   & 106  &   1.89  & 0           & 693             \\
		\bottomrule
	\end{tabular}
	\caption{Results summary of collision correctness experiments after the tolerance was exceeded}
	\label{tab_AboveTolerance}
\end{table}

@@

The more times thrashing occurs, the later the collision may be detected as objects continue to be updated and move without a collision occurring. It should be noted that thrashing occurring does not guarantee that a late collision will take place. The more times thrashing takes place, the more physics updates occur and the further the objects may be moved towards (and eventually overlapping) each other. Therefore, a greater number of times thrashed, means a late and incorrect collision response is more likely, but not guaranteed.

@@

\subsubsection{Evaluation - Speed}
As the speed increases, the proportion of late collisions to correct collisions increases, as shown in Figs. \ref{fig_RatioVsSpeedLow}, \ref{fig_RatioVsSpeedMid} and \ref{fig_RatioVsSpeedHigh}. When speed is below the speed tolerance, late collisions do not exceed 10\%. This 10\% is assumed to be caused by false-positives. Once above the speed tolerance, the proportion of late collisions increases immediately, which is predicted by the aura calculation. Missed collisions begin to occur when speed exceed $80ms^{-1}$ in the $48ms^{-1}$ experiment, this is due to objects travelling so quickly, the objects completely pass one another, missing the collision entirely.

@@

As the speed increases, the mean penetration time increases, as shown in Figs. \ref{fig_CollisionsPenVsSpeedLow}, \ref{fig_CollisionsPenVsSpeedMid} and \ref{fig_CollisionsPenVsSpeedHigh}. With the exception of the starting speed, the standard deviation remains constant below the tolerance line. Once speed increases above the tolerance line, the standard deviation initially increases, but appears to remain constant after the initial increase. 
%Note that the mean error increases in discrete steps (with some small variation), this is due to the discrete physics time-steps.

\subsubsection{Evaluation - Latency}
As the latency increases, the proportion of late collisions to correct collisions increases, as shown in Fig. \ref{fig_RatioVsLatencyHigh}. However, Figs. \ref{fig_RatioVsLatencyLow} and \ref{fig_RatioVsLatencyLow} do not show this relationship. In the $2ms$ latency tolerance experiment, late collisions do not exceed $20\%$, which is assumed to be accounted for by false-positives. The aura calculation predicts that late collisions should start occurring once $3ms$ has been exceeded, however, this is not observed, as the proportion does not increase above what would be expected for false-positives.
In the $8ms$ latency tolerance experiment, late collisions do not exceed $2\%$, which is assumed to be accounted for by false-positives. This remains the case even when the tolerance is exceeded. The aura calculation predicts that late collisions will not begin to occur until $20ms$ latency is reached, which this experiment does not reach, therefore no late collisions outside of false-positives are expected. In the $16ms$ latency tolerance experiment, late collisions do not exceed $3\%$ below the tolerance, which is assumed to be accounted for by false-positives. The aura calculation predicts that late collisions will not begin to occur until $20ms$ latency is reached. In Fig. \ref{fig_RatioVsLatencyHigh} we see the proportion of errors increase from $20ms$ and above, however, it does not exceed the expected false-positive proportion until $25ms$ latency is reached.
%TODO: Re-run latency experiment, larger sample size?

@@

\subsubsection{Evaluation - Frame-Time}
As frame-time increases, the proportion of late collisions to correct collisions increases, as shown in Figs. \ref{fig_RatioVsLatencyLow} and \ref{fig_RatioVsLatencyMid}, however in \ref{fig_RatioVsLatencyHigh} the sample size is small above the tolerance line due to the high occurrences of thrashing and so the relationship in this experiment can not be deduced. For the $8ms$ and $15ms$ experiments the late collisions do not exceed 10\% and is assumed to be accounted for by false-positives. In the $8ms$ frame-time tolerance experiment, late collisions are not expected to occur until $16ms$ frame-time, based on the aura size. Late collisions do not exceed $20\%$ and is assumed to be accounted for by false-positives. In the $15ms$ frame-time tolerance experiment, late collisions exceed $20\%$ once $16ms$ latency is exceeded as predicted by the aura size and increase to over $75\%$ at $30ms$ latency.
In the final frame-time tolerance experiment using $32ms$ frame-time tolerance, late collisions only occur for frame-times of $64ms$. The aura calculation predicts that late collisions should begin to occur as soon as $32ms$ frame-time is exceeded, however, due to the low sample size, as a result of the high occurrences of thrashing, the plot does not accurately represent any relationship between frame-time and proportion of late collisions.

For the first two frame-time experiments ($8.33ms$ and $15ms$ tolerance values), as frame-time increases, the mean penetration time increases and standard deviation also increases, shown in Figs. \ref{fig_CollisionsPenVsFrameTimeLow} and \ref{fig_CollisionsPenVsFrameTimeMid}. Standard deviation increases as the delay between frame-time update and physics update can always vary between 0 and the frame-time, meaning even in high frame-time situations, the delay between frame-time update and physics update can be 0. Exceeding the frame-time tolerance very quickly leads to high max error, this is due to the delay in messages being exchanged being created by the long frame-times on both servers (this is reflected in the aura calculation by the frame-time tolerance being multiplied by 2). However, as the target frame-time increases over the tolerance, variation in error increases and maximum errors become less likely. For the final frame-time experiment, ($33.33ms$ tolerance value), thrashing occurs the majority of the time both above (as demonstrated in \ref{tab_BelowTolerance} and \ref{tab_AboveTolerance}) and below the tolerance, due to this the results shown in \ref{fig_CollisionsPenVsFrameTimeHigh} have a very small sample size and thus will not accurately represent the relationship between frame-time and penetration.

\subsubsection{Varying Factors - Summary}
The varying factors experiments demonstrate that the aura calculation is conclusively correct for speed and frame-time aura tolerance factors and at minimum approximate for latency. For each varied factor, for all three tolerance values chosen, below the tolerance value, the mean + two standard deviations lies under the maximum penetration time expected on a centralised simulation, with only a small number of exceptions discussed above. These experiments also demonstrate the relationship between increasing the tolerance values and amount of thrashing expected to occur. There are no missed collisions, with the exception of the speed experiments, which have significantly fewer than $1\%$ misses below the tolerance and $1.12\%$ misses above the tolerance. Once factors increase above their respective tolerance values, late collisions begin to occur and the more the factors are exceeded, the number and magnitude of errors increase. This demonstrates the correctness of the aura calculation in AP.
%Therefore, we have shown that if the aura calculation factors remain within their respective tolerances, erroneous collisions will be small in magnitude and rare in number. %TODO: Summary Table: Row for each factor: Number of collisions below tolerance, Percentage of errors below tolerance, Mean error below tolerance

@@

In addition to varying each aura tolerance factor, an experiment was undertaken to determine the effects of packet-loss on the correctness of collisions between objects. In this experiment the packet-loss was varied from $0\%$ to $20\%$ in increments of $1\%$. The aura calculation does not account for packet-loss and and therefore there is no aura tolerance. Packet-loss is controlled using the Traffic Control tool; it is simulated on each server for all communication received from the other server.

@@

\subsubsection{Evaluation}
As packet-loss increases, late and erroneous collisions increase and late collisions increase in magnitude. This is due to messages being delayed as packets are lost and need to be re-sent by RakNet's reliability layer. Missed collisions begin to occur as soon as packet-loss exceeds $1\%$, but increase at a lower rate relative to late collisions. (Note, late collisions begin to occur from $0\%$, this is expected as all factors are set to be equal to their tolerances). These results demonstrate that AP is able to prevent $50\%$ of late collisions even in cases of packet-loss as high as (15\%) and prevent all missed collisions with up to $1\%$ packet-loss, which is much greater packet-loss than would be expected in practice (0.01\%) \cite{ThousandEyesCloudPerf2018}.
